
%\thispagestyle{empty}
%\mbox{}
\begin{thebibliography}{11}

\bibitem{Otra_Coorporativa}
\textsc{L. Briñon Arranz, A. Seuret, and C. Canudas de Wit,} 
\textit{" Cooperative Control Design for Time-Varying Formations of Multi-Agent Systems,"} IEEE Transactions on Automatic Control,Institute of Electrical and Electronics Engineers (IEEE), 2014, 59 (8), pp.2283-2288.

\bibitem{Control_Formacion}
\textsc{H. Garcia de Marina, Z. Sun, M. Bronz, and G. Hettenberger,} 
\textit{" Ciruclar Formation Control of Fixed-wing UAVs with Constant Speeds,"} Conference Paper - September 2017.

\bibitem{Aplicaciones_Militares}
\textsc{M. Ekelhof, and G. Persi Paoli,} (2020). Swarm Robotics: Technical and Operational Overview of the Next Generation of Autonomous Systems. [Online]. Available: \url{https://unidir.org/publication/swarm-robotics-technical-and-operational-overview-next-generation\\
-autonomous-systems}.

\bibitem{Aplicacion_2}
\textsc{Y. Tan, and Z.-y. Zheng,} 
\textit{"Research advance in swarm robotics,"} Defence Technology, vol. 9, no. 1, pp. 18-39, 2013. 

\bibitem{Aplicacion_3}
\textsc{G.-Z. Yang, D. Bellingham, P. Dupont, P. Fischer, L. Floridi, R. Full, N. Jacobstein, V. Kumar, M. McNutt, R. Merrifield, B. Nelson, B. Scassellati, M. Taddeo, R. Taylor, M. Veloso, Z. Wang, and R. Wood,} 
\textit{"The grand challenges of Science Robotics,"} Science Robotics, 3, eaar7650, 2018.

\bibitem{Aplicacion_4}
\textsc{E. Sahin,} 
\textit{"Swarm Robotics: From Sources of Inspiration to Domains of Application,"} Conference Paper in Lecture Notes in Computer Science, 2015.
\newpage
\bibitem{Estimacion_Gradiente}
\textsc{L. Briñón-Arranz, L. Schenato, Member, IEEE, and A. Seuret,} 
\textit{"Distributed Source Seeking via a Circular Formation of Agents Under Communication Constrains,"} IEEE Trans. on Control of Network Systems, vol. 3, no. 2, June 2014.

\bibitem{Git_Hector}
\textsc{H. Garcia de Marina, Z. Sun, M. Bronz, and G. Hettenberger,} (2021, Feb 12). Github [Online]. Available: \url{https://github.com/UCM-237/pyVehicles}

\bibitem{Adicional_Estimacion_1}
\textsc{L. Briñón-Arranz, A. Renzaglia, and L. Schenato,} 
\textit{"Multi-Robot Symmetric Formations for Gradient and Hessian Estimation with Application to Source Seeking,"} IEEE Trans. on Robotics, IEEE, 2019, 35 (3), pp.782-789.

\bibitem{Base_Coorporativa}
\textsc{Y. A. Kapitanyuk, A. V. Proskurnikov, and M. Cao,} 
\textit{"A guiding vector field algorithm for path following control of nonholonomic mobile robots,"} 2016, iEEE Transactions on Control System Technology, accepted. 

\bibitem{Git_todos}
\textsc{H. Garcia de Marina, J. F. Jiménez Castellano, and U. A. Ardizzi Rodríguez,} (2021, Feb 12). Github [Online]. Available: \url{https://github.com/uardizzi/pyVehicles}

\end{thebibliography}
